\documentclass{article}
\usepackage[left = 3cm, right = 3cm]{geometry}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\urlstyle{same}

\makeatletter
\renewcommand*{\UrlTildeSpecial}{%
  \do\~{%
    \mbox{%
      \fontfamily{ptm}\selectfont
      \textasciitilde
    }%
  }%  
}%    
\let\Url@force@Tilde\UrlTildeSpecial
\makeatother

\begin{document}
\begin{Huge}
\noindent Lihua Lei
\end{Huge}

\vspace{5mm}
\begin{minipage}{0.6\linewidth}
  \flushleft
\noindent Knight Management Center, Stanford University \\
\noindent Stanford, CA 94305-4020
\end{minipage}
\hfill
\begin{minipage}{0.4\linewidth}
  Website: \url{https://lihualei71.github.io}\\
  Email: \,\,\,\,\,lihualei@stanford.edu
\end{minipage}

\vspace{5mm}
\begin{large}
\noindent \textbf{Academic Appointments}
\end{large}
\vspace{5mm}

\begin{minipage}{0.65\linewidth}
  \noindent Assistant Professor of Economics \\
  Stanford Graduate School of Business\\

  \noindent Assistant Professor of Statistics (by courtesy) \\
  Department of Statistics\\

  \noindent Faculty Fellow \\
  Stanford Institute for Economic Policy Research \\

  \noindent Postdoctoral Researcher, Stanford University\\
  Advisor: Emmanuel Cand\`{e}s
\end{minipage}\hfill
\begin{minipage}{0.34\linewidth}
\flushright
\vspace{-3mm}
7/2022 - present\\
~\\
~\\
11/2022 - present\\
~\\
~\\
12/2022 - present\\
~\\
~\\
9/2019 - 7/2022 \\
\end{minipage}

\vspace{5mm}
\begin{large}
\noindent \textbf{Education}
\end{large}
\vspace{5mm}

\begin{minipage}{0.65\linewidth}
\noindent Ph.D. Statistics, University of California, Berkeley\\
Advisors: Peter, J. Bickel, and Michael, I. Jordan\\

\noindent B.S. Statistics, Peking University\\
Undergraduate Thesis Advisor: Song Xi, Chen\\

\noindent B.A. Economics (double major), Peking University

\end{minipage}\hfill
\begin{minipage}{0.34\linewidth}
\flushright
\vspace{-1mm}
8/2014 - 8/2019 \\
~\\
~\\
9/2010 - 6/2014\\
~\\
~\\
9/2011 - 6/2014\\
\end{minipage}

\vspace{5mm}
\begin{large}
\noindent \textbf{Research}
\end{large}
\vspace{5mm}


\begin{large}
\noindent Journal Publications \footnote{$\ast$ = alphabetical ordering or equal contribution}
\end{large}

\begin{enumerate}
\item Luo, Y., Fithian, W, and \textbf{Lei, L.} (2022) Improving knockoffs with conditional calibration. \emph{Arxiv e-prints, abs/2208.09542}. Accepted at \emph{Annals of Statistics (AoS)}.  
\item Angelopoulos, A.*, Bates, S.*, Cand\`{e}s, E. J.*, Jordan, M. I.*, and \textbf{Lei, L.}* (2025) Learn then Test: Calibrating Predictive Algorithms to Achieve Risk Control. \emph{Annals of Applied Statistics (AoAS)}, 19(2), 1641-1662
\item \textbf{Lei, L.}* (2024) Discussion of ”Data Fission: Splitting a Single Data Point” – Some Asymptotic Results for Data Fission. \emph{Journal of the American Statistical Association (JASA), 120(549), 147-150,} (invited discussion paper).
\item Arkhangelsky, D., Imbens, G., \textbf{Lei, L.}, and Luo, X. (2024) Design-Robust Two-Way-Fixed-Effects Regression For Panel Data. \emph{Quantitative Economics (QE)}, 15(4), 999-1034.
\item Marandon, A., \textbf{Lei, L.}, Mary, D., and Roquain, R. (2024) Adaptive novelty detection with false discovery rate guarantee. \emph{Annals of Statistics (AoS)}, 52(1), 157-183.
\item Spector, A., Cand\`{e}s, E. J.*, \textbf{Lei, L.}* (2023) A Discussion of Tse and Davidson (2022) “A Note on Universal Inference”. \emph{Stat}, 12(1)
\item Bates, S.*, Cand\`{e}s, E. J.*, \textbf{Lei, L.}*, Romano, Y.*, and Sesia, M.* (2022) Testing for Outliers with Conformal p-values. \emph{ArXiv e-prints, abs/2104.08279}. \emph{Annals of Statistics (AoS)}, 51(1), 149-178.  
\item Cand\`{e}s, E. J.*, \textbf{Lei, L.}*, Ren, Z.* (2022) Conformalized Survival Analysis. \emph{ArXiv e-prints, abs/2103.09763}. \emph{Journal of the Royal Statistical Society: Series B (JRSS-B)}, 85(1), 24-45.
\item Horv\'{a}th, S.*, \textbf{Lei, L.}*, Richt\'{a}rik, P., and Jordan, M. I. (2022) Adaptivity of Stochastic Gradient Methods for Nonconvex Optimization. \emph{SIAM Journal on Mathematics of Data Science (SIMODS)}, 4(2), 634-648.
\item Fithian, W. and \textbf{Lei, L.} (2022) Conditional calibration for false discovery rate control under dependence. \emph{Annals of Statistics (AoS)}, 50(6), 3091-3118.
\item Bates, S.*, Angelopoulos, A.*, \textbf{Lei, L.}*, Malik, J., and Jordan, M. I. (2021) Distribution-Free, Risk-Controlling Prediction Sets. \emph{Journal of the ACM (JACM)}, 68(6), 1–34.
\item Loper, J. H.*, \textbf{Lei, L.}*, Fithian, W., and Tansey, W. (2021) Smoothed Nested Testing on Directed Acyclic Graphs. \emph{Biometrika}, 109(2), 457-471.
\item \textbf{Lei, L.} and Cand\`{e}s, E. J. (2021) Conformal Inference of Counterfactuals and Individual Treatment Effects. \emph{Journal of the Royal Statistical Society: Series B (JRSS-B)}. 83(5), 911-938.
\item \textbf{Lei, L.} and Ding, P. (2020) Regression Adjustment in Randomized Experiments With A Diverging Number of Covariates. \emph{Biometrika}. 108(4), 815-828.
\item Li, T., \textbf{Lei, L.}, Bhattacharyya, S., Van den Berge, K., Sarkar, P., Bickel, P. J., and Levina, E. (2020) Hierarchical community detection by recursive partitioning. \emph{Journal of the American Statistical Association (JASA)} 117(538), 951-968.
\item \textbf{Lei, L.} and Bickel, P. J. (2020) An Assumption-Free Exact Test For Fixed-Design Linear Models With Exchangeable Errors. \emph{Biometrika}, 108(2), 397-412.
\item \textbf{Lei, L.}, Ramdas, A., and Fithian, W. (2020) A general interactive framework for FDR control under structural constraints. \emph{Biometrika}, 108(2), 253-267.
\item \textbf{Lei, L.} and Jordan, M. I. (2020) On the Adaptivity of Stochastic Gradient-Based Optimization. \emph{SIAM Journal on Optimization (SIOPT)}, 30(2), 1473-1500.
\item D'Amour, A., Ding, P., Feller, A., \textbf{Lei, L.}, and Sekhon, J. (2019) Overlap in High Dimensional Observational Studies. \emph{Journal of Econometrics (JoE)}, 221(2), 644-654.
\item \textbf{Lei, L.}, and Fithian, W. (2018). AdaPT: An Interactive Procedure For Multiple Testing With Side Information. \emph{Journal of the Royal Statistical Society: Series B (JRSS-B)}, 80(4), 649-679.
\item \textbf{Lei, L.}, Bickel, P. J., and El Karoui, N. (2018). Asymptotics For High Dimensional Regression M-Estimates: Fixed Design Results. \emph{Probability Theory and Related Fields (PTRF)}, 172(3-4), 983-1079.
\item Chen, S. X., \textbf{Lei, L.}, and Tu, Y. (2016). Functional Coefficient Moving Average Model with Applications to forecasting Chinese CPI. \emph{Statistica Sinica}, 26, 1649-1672.
\end{enumerate}

\begin{large}
\noindent Conference Publications
\end{large}

\begin{enumerate}
\item Li, X., Li, Y., Zhong, H., \textbf{Lei, L.} and Deng, Z. (2025). Statistical Inference under Performativity. arXiv preprint. In \emph{The 39th of Annual Conference on Neural Information Processing Systems (NeurIPS)}.
\item Chen, C., Shen, J., Deng, Z., \textbf{Lei, L.} (2025) Conformal Tail Risk Control for Large Language Model Alignment. In \emph{Proceedings of the 42th International Conference on Machine Learning (ICML)}.
\item Wang, W., Janson, L., \textbf{Lei, L.}, and Ramdas, A. (2024) Total Variation Floodgate for Variable Importance Inference in Classification. In \emph{Proceedings of the 41th International Conference on Machine Learning (ICML)}.
\item Angelopoulos, A.*, Bates, S.*, Fisch, A.*, \textbf{Lei, L.}*, and Schuster T.* (2023) Conformal Risk Control. In \emph{International Conference on Learning Representations (ICLR)}.
\item Elibol, M., \textbf{Lei, L.}, and Jordan, M. I. (2020). Variance Reduction with Sparse Gradients. In \emph{International Conference on Learning Representations (ICLR)}.
\item Ye, Y., \textbf{Lei, L.}, and Ju, C. (2018). HONES: A Fast and Tuning-free Homotopy Method For Online Newton Step. In \emph{Proceedings of the 20th International Conference on Artificial Intelligence and Statistics (AISTATS)}.
\item \textbf{Lei, L.}, Ju, C., Chen, J., and Jordan, M. I. (2017). Nonconvex Finite-Sum Optimization Via SCSG Methods. In \emph{Proceedings of the 30th Advances in Neural Information Processing Systems (Neurips)}.
\item \textbf{Lei, L.} and Jordan, M. I. (2017). Less than a Single Pass: Stochastically Controlled Stochastic Gradient. In \emph{Proceedings of the 20th International Conference on Artificial Intelligence and Statistics (AISTATS)}.
\item \textbf{Lei, L.} and Fithian, W. (2016). Power of Ordered Hypothesis Testing. In \emph{Proceedings of the 33th International Conference on Machine Learning (ICML)}.
\end{enumerate}

\begin{large}
\noindent Under Revision
\end{large}

\begin{enumerate}
\item \textbf{Lei, L.}* and Ross, B.* (2023) Estimating Counterfactual Matrix Means with Short Panel Data. \emph{Arxiv e-prints, abs/2312.07520}. Under Reject and Resubmit at \emph{Econometrica}.
\item Ji, W.*, \textbf{Lei, L.}*, and Spector A.* (2023) Model-Agnostic Covariate-Assisted Inference on Partially Identified Causal Effects. \emph{Arxiv e-prints, abs/2310.08115}. Under Major Revision at \emph{Journal of Political Economy (JPE)}.
\item Sahoo, R., \textbf{Lei, L.}, and Wager, S. (2022) Learning from a Biased Sample. \emph{Arxiv e-prints, abs/2209.01754}. Under Minor Revision at \emph{Management Science (MS)}.  
\item Ji, W.*, \textbf{Lei, L.}*, and Zrnic, T.* (2025) Predictions as surrogates: Revisiting surrogate outcomes in the age of AI. \emph{ArXiv preprint abs/2501.09731}. Under Major Revision at \emph{Biometrika}.
\item Hartog, W.*, \textbf{Lei, L.}* (2025) Family-wise error rate control with e-values. \emph{ArXiv preprint abs/2501.09015}. Under Major Revision at \emph{Annals of Statistics (AoS)}.
\item Luo, Y., Fithian, W. and \textbf{Lei, L.} (2024) Estimating the FDR of variable selection. \emph{Arxiv e-prints, abs/2408.07231}. Under Major Revision at \emph{Annals of Statistics (AoS)}.
\end{enumerate}

\begin{large}
\noindent Preprints and Submissions
\end{large}

\begin{enumerate}
\item Chen, J.*, \textbf{Lei, L.}*, Sudijono, T*., Sun, L.*, and Xie, T*. (2025) Compound Selection Decisions: An Almost SURE Approach. \emph{Arxiv e-prints, abs/2511.11862}
\item Ji, W., Pan, Y., Zhu, R. and \textbf{Lei, L.} (2025) Multi-Armed Bandits With Machine Learning-Generated Surrogate Rewards. \emph{Arxiv e-prints, abs/2506.16658}.
\item \textbf{Lei, L.} (2024) Causal Interpretation of Regressions With Ranks. \emph{Arxiv e-prints, abs/2406.05548}.
\item Yang, Z., \textbf{Lei, L.}, and Cand\`{e}s, E. J. (2024) Bellman Conformal Inference: Calibrating Prediction Intervals For Time Series. \emph{Arxiv e-prints, abs/2402.05203}.
\item \textbf{Lei, L.}* and Sudijono, T.* (2024) Inference for Synthetic Controls via Refined Placebo Tests. \emph{Arxiv e-prints, abs/2401.07152}.
\item Viviano, D., \textbf{Lei, L.}, Imbens, G., Karrer, B., Schrijvers, O., and Shi, L. (2023) Causal clustering: design of cluster experiments under network interference. \emph{Arxiv e-prints, abs/2310.14983}.
\item Andrews, I., Fudenberg, D., \textbf{Lei, L.}, Liang A., and Wu. C. (2023) The Transfer Performance of Economics Models. \emph{Arxiv e-prints, abs/2202.04796}. (Accepted at EC 2025)
\item \textbf{Lei, L.}*, Sahoo, R.*, and Wager, S.* (2023) Policy Learning under Biased Sample Selection. \emph{Arxiv e-prints, abs/2304.11735}.  
\item \textbf{Lei, L.} and Wooldridge, J. (2022) What Estimators Are Unbiased For Linear Models? \emph{Arxiv e-prints, abs/2212.14185}.
\item Yang, C., \textbf{Lei, L.}, Ho, N., and Fithian, W. (2021) BONuS: Multiple multivariate testing with a data-adaptive test statistic. \emph{ArXiv e-prints, abs/2106.15743}.
\item \textbf{Lei, L.}*, Li, X.*, and Lou, X.* (2020) Consistency of Spectral Clustering on Hierarchical Stochastic Block Models. \emph{ArXiv e-prints, abs/2004.14531}.
\item \textbf{Lei, L.} (2019) Unified $\ell_{2\rightarrow\infty}$ Eigenspace Perturbation Theory for Symmetric Random Matrices. \emph{ArXiv e-prints, abs/1909.04798}.
\end{enumerate}

\begin{large}
\noindent Software
\end{large}

\begin{enumerate}
\item \texttt{adaptMT}: \texttt{R} package on Adaptive P-value Thresholding (on CRAN);
\item \texttt{cfcausal}: \texttt{R} package on conformal inference of counterfactuals and individual treatment effects (on github);
\item \texttt{dbh}: \texttt{R} package on dependence-adjusted Benjamini-Hochberg and general step-up procedures (on github);
\item \texttt{mkn}: \texttt{R} package on multiple knockoffs based inference (on github).
\item \texttt{ovalue}: \texttt{R} package on distribution-free assessment of population overlap (O-values) for observational studies (on github).
\item \texttt{transferUQ}: \texttt{R} package on uncertainty quantification of transfer performance for prediction models
\end{enumerate}

\vspace{3mm}
\begin{large}
\noindent \textbf{Awards}
\end{large}

\vspace{5mm}

ICSA Outstanding Young Reseacher Award, 2025.

\vspace{2mm}

Bernoulli Society New Reseacher Award, 2025.

\vspace{2mm}

NSF CAREER award, 2024.

\vspace{2mm}

Fletcher Jones Faculty Scholar for 2023-24. 

\vspace{2mm}

ICSA Junior Research Award, 2022.

\vspace{2mm}

IMS (Institute of Mathematical Statistics) New Researcher Travel Award, 2022.

\vspace{2mm}

Rising Star in Data Science (University of Chicago), 2021.

\vspace{2mm}

Eric Lehmann Citation (Annual Dissertation Award in Theoretical Statistics), 2019.

\vspace{2mm}

Citadel Fellowship, 2017-2018.

\vspace{2mm}

Outstanding Graduate Student Instructor Award, 2016.

\vspace{2mm}
ICML (International Conference on Machine Learning) Travel Award, 2016.

\vspace{2mm}
ACIC (Atlantic Causal Inference Conference) Travel Award, 2018, 2022.

\vspace{2mm}
Scholarship from The Sally and Terry Speed Graduate Support Fund, 2015.

\vspace{5mm}

\begin{large}
\noindent \textbf{Invited Talks}
\end{large}

\vspace{4mm}
\noindent 2025: Joint Statistical Meetings (JSM), Workshop on ``Econometrics at Emory: Causal Inference with Panel Data'' (Emory), Princeton (Econ), Berkeley (Econ), Duke (Decision Sciences), Southern Economic Association (SEA) Annual Meeting, Washington University in St. Louis (Stats).

\vspace{4mm}
\noindent 2024: UBC (Marketing, Stats, Econ), SFU (Econ), NYU (Econ), UCLA (Econ), NorCal Junior Econometricians' Conference (UCSC), Cowles Foundation Summer Conference in Econometrics (Yale), Workshop of Statistical Network Analysis and Beyond (SNAB 2024), Pacific Causal Inference Conference (PCIC), EcoSta Conference, Joint Conference on Statistics and Data Science (JCSDS), 2024 Shanghai Workshop on Robustness Meets Causality, NBER Summer Institute (Labor Studies), Upenn (Econ, Stats), PennState (Econ), MIT (IDSS), David Simchi-Levi's group (MIT), Wisconsin (Econ), UW (Econ), Southern Economic Association (SEA) Annual Meeting, International Conference on Statistics and Data Science (ICSDS).

\vspace{4mm}
\noindent 2023: McGill (Stats), UNC Kosorok PHAIR Lab, Cornell (Stats), University of Warwick (Guest lecture), Econometrics in the Era of Machine Learning (University of Chicago), Columbia (IEOR and DRO), Rutgers (Econ), Peking University (Stats), Clubear, Brown (Econ), NorCal Junior Econometricians' Conference (UC Davis), Workshop of Statistical Network Analysis and Beyond (SNAB 2023), Yale (Econ), Columbia (Econ), Northwestern (Econ), UChicago (Econ), Southern Economic Association (SEA) Annual Meeting.

\vspace{4mm}
\noindent 2022: Chamberlain Econometrics Seminar, Online Causal Inference Seminar, UC Berkeley (Econ), Joint Statistical Meetings, ICSA China Conference, Workshop on Interactive Causal Learning, IMS Annual in Probability and Statistics, Simons Institute for the Theory of Computing (UC Berkeley), New England Statistics Symposium, Tsinghua IIIS Seminar on Foundations Of Data Science, UNC CIRG Seminar, AEA/ASSA Annual Meeting

\vspace{4mm}
\noindent 2021-22 job talks: University of Michigan (Stats), USC (Math), Rutgers (Stats), NYU Courant (Data Science), USC(Stats), University of Minnesota (Stats), Northwestern (Stats), Stanford GSB (Econ), Columbia (Stats), UPenn Wharton (Stats), CMU (Stats), Harvard (Stats), University of Chicago (Data Science), Chicago Booth (Econometrics), Purdue (Stats), UC Berkeley (Stats), Yale (Stats)

\vspace{4mm}
\noindent 2021: One World YoungStatS Webinar, Journal of Royal Statistical Society Webinar, Stanford Causal Inference Group, University of Washington (Stats), UC Davis (Econ), Harvard (Econ), Temple University (Stats), NYU Data Science Lunch Seminar, ICSA Applied Statistics Symposium, International Conference on Multiple Comparison Procedures, ICML Workshop on "Neglected Assumptions of Causal Infernece", IFDS Summer Workshop, INFORMS Virtual Healthcare Conference, The Hong Kong University of Science \& Technology (Stats), WNAR Annual Meeting, ETH Z\"{u}rich (Data Science), UC Berkeley (Stats), Stanford (Stats), University of Chicago (Stats), Stanford RAIN Seminar, UChicago Crime Lab, Chicago Booth (Econometrics), University of Maryland, Baltimore County (Stats), Dataiku Research, Northwestern (Biostats, Stats), University of Manchester (Biostats), The London School of Hygiene \& Tropical Medicine, Computer Vision Talks Webinar, Facebook Core Data Science, UCLA (Big Data and ML), University of Missouri (Biostats), Leiden Univerity, Twitter, Stitch Fix, Rutgers (Stats), UPenn Wharton (Stats)

\vspace{4mm}
\noindent 2020:
Lyft, John Hopkins University Causal Inference Group, Florida State University (Guest Lecture), UC Berkeley (Guest Lecture), University of North Carolina at Chapel Hill (Biostats), Peking University (Biostats), Pacific Causal Inference Conference, Online Causal Inference Seminar, International Seminar on Selective Inference, Southwestern University of Finance and Economics, BAAI Conference, Stanford University (Journal Club), Stanford Data Studio, UC Berkeley (Guest Lecture), WNAR Annual Meeting, UC Berkeley Causal Inference Group

\vspace{4mm}
\noindent 2019: SAMSI Workshop, Facebook Core Data Science, Berkeley-Stanford Econometrics Jamboree, Joint Statistical Meetings, ICSA Applied Statistics Symposium, Yale (Polisci), UC Davis (Stats), Stanford University (Guest Lecture)

\vspace{4mm}
\noindent 2018: USC (Stats), University of Michigan (Guest Lecture), University of Michigan (Stats), International Conference on Econometrics and Statistics, Atlantic Causal Inference Conference, UC Davis (Guest Lecture), Stanford University (Guest Lecture)

\vspace{4mm}
\noindent 2017: Berkeley-Stanford Econometrics Jamboree
 

% \begin{large}
% \noindent Contributed Talks and Poster Presentation
% \end{large}

% \vspace{2mm}
% Workshop on Higher-Order Asymptotics and Post-Selection Inference (WHOA-PSI), 2018.

% \vspace{2mm}
% European Causal Inference Meeting (EuroCIM), 2018.

% \vspace{2mm}
% Neural Information Processing Systems (NIPS), 2017.

% \vspace{2mm}
% International Conference on Multiple Comparison Procedures (MCP), 2017.

% \vspace{2mm}
% International Conference on Artificial Intelligence and Statistics (AISTATS), 2017.

% \vspace{2mm}
% Joint Statistical Meetings (JSM), 2016, 2018.

% \vspace{2mm}
% International Conference on Machine Learning (ICML), 2016.

% \vspace{2mm}
% Stanford-Berkeley Joint Colloquium, 2015, 2016, 2017.

% \vspace{2mm}
% Berkeley Statistics Annual Research Symposium (BSTARS), 2017, 2018.

% \newpage
\vspace{7mm}
\begin{large}
\noindent \textbf{Reviewing}\footnote{reviews of revisions not included}
\end{large}

\vspace{2mm}
\noindent \textbf{Statistics Journals (87): }(\#papers in parentheses) Annals of Statistics (AoS, 21), Journal of the American Statistical Association (JASA, 14), Biometrika (13), Journal of the Royal Statistical Society-Series B (JRSS-B, 11), Journal of the Royal Statistical Society-Series A (JRSS-A, 1), Bernoulli (2), Electronic Journal of Statistics (EJS, 5), Biometrics (3), Journal of Causal Inference (JCL, 2), Stat (1), Springer Book (1), SpringerBriefs (1), International Journal of Biostatistics (IJB, 1), Journal of Computational and Graphical Statistics (JCGS, 2), Statistica Sinica (3), International Journal of Approximate Reasoning (IJA, 1), Statistics in Biosciences (SIBS, 1), Journal of Statistical Planning and Inference (JSPI, 2), Statistical Science (SS, 2), Statistics (1)

\vspace{2mm}
\noindent \textbf{Economics Journals (34): }(\#papers in parentheses) Econometrica (5), Journal of Political Economy (JPE, 7), The Quarterly Journal of Economics (QJE, 1), Review of Economic Studies (ReStud, 2), JPE Mirco (3), The Review of Economics and Statistics (ReStat, 7), Journal of Applied Econometrics (JAE, 1), Journal of Business and Economic Statistics (JBES, 2), Journal of Econometrics (JoE, 6)

\vspace{2mm}
\noindent \textbf{Other Journals (26): } Proceedings of the National Academy of Sciences of the United States of America (PNAS, 2), SIAM Journal on Mathematics of Data Science (SIMODS, 1), Operations Research (1), Management Science (1), Journal of Machine Learning Research (JMLR, 9), Transactions on Pattern Analysis and Machine Intelligence (TPAMI, 3), Computational Optimization and Applications (COAP, 1), Optimization Methods and Software (GOMS, 1), Artificial Intelligence (1), Information and Inference: A Journal of the IMA (IMAIAI, 2), Vietnam Journal of Mathematics (VJOM, 1), IEEE Transactions on Information Theory (1), American Journal of Epidemiology (AJE, 1), BMC Medical Research Methodology (1)

\vspace{2mm}
\noindent \textbf{Conferences: }(year in parentheses) ICML (2019, 2020, 2021), NeurlPS (2019, 2020, 2021), COLT (2019, 2020, 2021), AISTATS (2019), UAI (2020, 2021)

\vspace{7mm}
\begin{large}
\noindent \textbf{Other Academic Services}
\end{large}

\begin{itemize}  
\item Co-organizer of the International Seminar on Selective Inference (with Will Fithian, Rina Barber, and Jelle Goeman, 2020-present).
\item Co-organizer of the Causal Panel Data Conference (with Bryan Graham, Guido Imbens, and Jann Spiess, 2023).
\item Institute of Mathematical Statistics (IMS) Committee on Nomations. 
\item Co-organizer of the GRoup-Of-Why (GROW) seminar, a causal reading group at Stanford University (with Guillaume Basse and Dominik Rothenhäusler, 2019).
\item Invited panelist at ``IMS NRG Virtual Panel: Navigating the Academic Job Market'' (2024)
\end{itemize}

\end{document}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
